On the Design, Use and Removal of Eval in R

### 2020-08-10 main.tex
Added some comments to the paper

\section{Introduction}
\textbf{*}

@@

\subsection{How are they used}
\textbf{Pierre}

@@

\section{Related Work}
\textbf{Aviral}

>>>>

\section{Introduction}
- Why eval is used in R
- What the community says about using eval
- What existing tools do about eval
- Do people use eval for obvious things like looking up variable, if yes, it is
because they are unaware of alternatives?
- Why automating the transformation is a hard problem.
- What is the goal of the work? To replace eval with code for static analyssi or
for consumption by the users of the language?
- We only permit transformations that preserve code behavior?
- Do we accept overly complex code as the output?

Why do we do this dynamically? Because it raises a chicken-and-egg problem,
doing it statically would require us to reason about eval based code which may
not be possible in general.

What are the challenges? Why is it not trivial?
- Do we handle aliasing of eval?
- Simple cases can be subtle? (laziness for ex.

Why can't we replace eval(code) by code?

Intended user of the technique? Which version of R is targeted.

Contributions:
- Describe the use of eval in R
- Develop a tool to replace evals guided by dynamic traces

- cannot replace with (cite study of with construct).
\textbf{*}

@@

\subsection{How are they used}
\textbf{Pierre}
- classify evals based on what they can be replaced with

@@

\section{Evaluation}

\section{Related Work}
\eval has been widely discussed in the research literature for the challenges it
imposes for code comprehension and automated code analyses.
Perhaps, \citeit{EvalMenDo} is the most popular exposition of \eval and its
challenges for JavaScript.

\textbf{Aviral}
- javascript
- ruby
- php
